### 2020-04-28 Paper/paper.tex
moved paper files to master

% AUTHOR NAMES GOES HERE
\author{
\IEEEauthorblockN{Shawn Mace}
\IEEEauthorblockA{\textit{Department of Computer Science} \\
\textit{Middle Tennessee State University}\\
Murfreesboro, United States \\
sdm2w@mtmail.mtsu.edu}\\
\IEEEauthorblockN{Derrick Reckers}
\IEEEauthorblockA{\textit{Department of Computer Science} \\
\textit{Middle Tennessee State University}\\
Murfreesboro, United States \\
dmr3p@mtmail.mtsu.edu}\\
\and
\IEEEauthorblockN{Aric Moilanen}
\IEEEauthorblockA{\textit{Department of Physics and Astronomy} \\
\textit{Middle Tennessee State University}\\
Murfreesboro, United States \\
atm4w@mtmail.mtsu.edu}\\
\IEEEauthorblockN{Jarrett Shaver}
\IEEEauthorblockA{\textit{Department of Computer Science} \\
\textit{Middle Tennessee State University}\\
Murfreesboro, United States \\
Jarrett.shaver@gmail.com}\\
\and
\IEEEauthorblockN{Matthew Ogden}
\IEEEauthorblockA{\textit{Department of Computer Science} \\
\textit{Middle Tennessee State University}\\
Murfreesboro, United States \\
email address}\\
\IEEEauthorblockN{Devon Wilson}
\IEEEauthorblockA{\textit{Department of Computer Science} \\
\textit{Middle Tennessee State University}\\
Murfreesboro, United States \\
email address}\\
}
\maketitle

@@

Start typing here \cite{b1}.

@@

Start typing here \cite{b2}.

@@

Our data was pulled from Galaxy Zoo: Mergers. This citizen scientist project had people view models for 62 pairs of colliding galaxies and choose which model best fit the taget galaxy image. The selected models were then put through a tournament system in which people would continue to select which model they believed to be best. After this tournament, each model was then assigned a score from 0 to 1 which represented how often it had been picked as the best model in the tournament. For example, a model with a score of 0.95 was chosen to be the best in 95\% of its tournament rounds.

>>>>

% AUTHOR NAMES GOES HERE
\author{
\IEEEauthorblockN{Shawn Mace}
\IEEEauthorblockA{\textit{Department of Computer Science} \\
\textit{Middle Tennessee State University}\\
Murfreesboro, United States \\
sdm2w@mtmail.mtsu.edu}\\
\IEEEauthorblockN{Derrick Reckers}
\IEEEauthorblockA{\textit{Department of Computer Science} \\
\textit{Middle Tennessee State University}\\
Murfreesboro, United States \\
dmr3p@mtmail.mtsu.edu}\\
\and
\IEEEauthorblockN{Aric Moilanen}
\IEEEauthorblockA{\textit{Department of Physics and Astronomy} \\
\textit{Middle Tennessee State University}\\
Murfreesboro, United States \\
atm4w@mtmail.mtsu.edu}\\
\IEEEauthorblockN{Jarrett Shaver}
\IEEEauthorblockA{\textit{Department of Computer Science} \\
\textit{Middle Tennessee State University}\\
Murfreesboro, United States \\
Jarrett.shaver@gmail.com}\\
\and
\IEEEauthorblockN{Matthew Ogden}
\IEEEauthorblockA{\textit{Computational Science, PhD Program} \\
\textit{Middle Tennessee State University}\\
Murfreesboro, United States \\
mbo2d@mtmail.mtsu.edu}\\
\IEEEauthorblockN{Devon Wilson}
\IEEEauthorblockA{\textit{Department of Computer Science} \\
\textit{Middle Tennessee State University}\\
Murfreesboro, United States \\
email address}\\
}
\maketitle

@@

When two galaxies merge, it causes a drastic change in the
evolution of the resulting galaxy. Understanding ongoing
collisions in the night sky, will aid scientists in their exploration
to uncover more about merging galaxies. Unfortunately,
information such as orbital velocities, orientations, and mass-ratios between the two galaxies cannot be obtained from
observation alone.

To obtain this information, past research has looked into
modeling the dynamics of interacting galaxies and developing
galactic models to simulate galaxy interactions. By finding
models and analyzing how well they fit known observations of
galaxies, models that “best fit” observations could reflect the
true parameters for the galaxy collisions.

This project takes data from galactic models and associated
human fitness scores, with the goal to develop several Neural
Network Tools that help scientists better understand this
data, and develop a machine fitness score that matches the
human fitness score. By having theses tools, scientists can
quicken the search to find those well-fitting models, explore
the galactic model parameter space, and hopefully find the
true dynamic parameters for observable galaxy collisions.

@@

Our project is based on several pieces of research. First is
the work of Toomre and Toomre who demonstrated merging
galaxies would cause distinct tidal distortions \cite{Toomre}. These tidal
distortions often result in the galaxies forming “bridges” and
“tails”, star regions that appear to bridge the gap between the
two galaxies, and arc away from each other. Toomre and
Toomre performed a variety of simulations showing that the
gravitation interactions caused these distinct shapes \cite{Toomre}.

Second is the work of SPAM. SPAM is O(n) public release
software that builds upon the restricted three-body model to
simulate galactic models merging. SPAM takes galactic
models and simulates the two galaxies merger. In addition,
point particles are added, undergoing realistic tidal distortions
and produce the iconic bridge and tail shapes \cite{WallinJSPAM}.

Lastly, most of our data has origins from Galaxy Zoo:
Mergers. Galaxy Zoo: Mergers is a citizen scientist effort to
explore the unknown parameter space for the galactic models.
Using the quick efficiency of SPAM to visual the final shape of
galactic models, millions of galactic models were simulated
and views by thousands of volunteers. Citizen scientists would
select models with a similar shape to the target image the
models are attempting to represent. From there, those
selected models went through a tournament like competition
with other models to receive the human fitness score. The
citizen scientist would choose the galactic model whose shape
better matches the target images. After going through the
tournament, all the models would have an associated fitness
scores \cite{WallinGalaxyZoo}.

The galactic models and their associated human fitness
score are what were used in this project. The human fitness
scores were directly applied, while the galactic models had to
be visualized again. The galactic models were sent through
SPAM again with a larger number of particles to obtain a 
higher resolution image of the colliding galaxies. These model
images and the human fitness scores are used \cite{WallinJSPAM}\cite{WallinGalaxyZoo}.

@@
